% Acknowledgements

\pdfbookmark[1]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer

\begin{flushright}{\slshape    
If you want to learn constructing, \\
build your own house.} \\ \medskip
--- \emph{unknown}
\end{flushright}

\bigskip

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements} % Acknowledgements section text

\noindent Many thanks to everybody who inspired me to finish this project! 
Especially to my family who endlessly encourage me to achieve every goals of my life.  \\

\noindent Special thanks to \emph{Mr. Ng\d{o}c-Quang Nguy\~{\^{e}}n} for technical advices regarding to the thesis' topic and related knowledge. \\

\noindent Regarding the project work, documentation and other help, many thanks go to \emph{Mr.Paavo Nevalainen}\footnote{\emph{PhD student}, University of Turku,  Dept. of Information Technology}. you are such a helpful and truly kind supervisor! \\

\noindent To \emph{Srinidhi Sun}\footnote{\emph{Master student}, University of Turku,  Dept. of Information Security}, thank you for your comments, and being such a good friend! \\

%\noindent Regarding the project \emph{layout design}: the layout was initially done by myself, which is used as demonstration in this paper, and redesigned by \emph{Th\`{u}y-Linh Nguy\~{\^{e}}n}.
Thank you very much for your impressive work.\\

\noindent Regarding the document template, I used the \latex template \emph{Classicthesis Typographic Thesis} of \emph{Andr\'{e} Miede}\footnote{http://www.miede.de}.
Thank you for your work and contributions to \latex community.\\

\noindent And finally, many thanks to the programming community for supports, knowledge, and best practices contributed to the whole community.

\endgroup
